### 2016-11-02 Manuscript/SW_early_life_telomeres.Rmd
Eds

#####Early-life telomere dynamics and survival
Early-life RTL was not related to survival to adulthood (estimate = `r round2(summary(glmer(SurvivedNext~cenTL+Agemonths+(1|PlateID)+(1|TerritoryID)+(1|FieldPeriodID),data=juv14,family = 'binomial'))$coefficients[2,1])`; P = `r round2(summary(glmer(SurvivedNext~cenTL+Agemonths+(1|TerritoryID)+(1|FieldPeriodID),data=juv14,family = 'binomial'))$coefficients[2,4])`), with no interaction effect between RTL and juvenile age (estimate = `r round2(summary(glmer(SurvivedNext~RTL*Agemonths+(1|TerritoryID)+(1|FieldPeriodID),data=juv14,family = 'binomial'))$coefficients[4,1])`; P = `r round2(summary(glmer(SurvivedNext~RTL*Agemonths+(1|TerritoryID)+(1|FieldPeriodID),data=juv14,family = 'binomial'))$coefficients[4,4])`), suggesting that there were no age-specific effects of juvenile RTL on survival to adulthood. To test whether cohort-level effects on RTL influenced survival we calculated cohort-level RTL (i.e. the median RTL for each cohort) and added this term to a GLMM, and found that cohort-level RTL was not related to survival to adulthood (estimate = `r round2(summary(glmer(SurvivedNext~cohortTL+RTL+Agemonths+(1|TerritoryID)+(1|FieldPeriodID),data=juv14,family = 'binomial'))$coefficients[2,1])`; P = `r round2(summary(glmer(SurvivedNext~cohortTL+RTL+Agemonths+(1|TerritoryID)+(1|FieldPeriodID),data=juv14,family = 'binomial'))$coefficients[2,4])`).

@@

temp <- subset(dd3,BirdID %in% juv$BirdID)
nrow(temp)

>>>>

#####Telomere dynamics and survival
Early-life RTL was not related to survival to adulthood (estimate = `r round2(summary(glmer(SurvivedNext~RTL+LogAge+(1|PlateID)+(1|TerritoryID)+(1|LayYear),data=dd14,family = 'binomial'))$coefficients[2,1])`; P = `r round2(summary(glmer(SurvivedNext~RTL+LogAge+(1|TerritoryID)+(1|LayYear),data=dd14,family = 'binomial'))$coefficients[2,4])`), with no interaction effect between RTL and  age (estimate = `r round2(summary(glmer(SurvivedNext~RTL*LogAge+(1|TerritoryID)+(1|LayYear),data=dd14,family = 'binomial'))$coefficients[4,1])`; P = `r round2(summary(glmer(SurvivedNext~RTL*LogAge+(1|TerritoryID)+(1|LayYear),data=dd14,family = 'binomial'))$coefficients[4,4])`), suggesting that there were no age-specific effects of juvenile RTL on survival to adulthood.

summary(glmer(SurvivedNext1~DeltaRTL+LogAge+(1|LayYear),data=dd3,family = 'binomial'))

@@
